IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/abstract.tex
haskell in the intro

\begin{abstract}
Many important security problems in JavaScript, such as browser
extension security, untrusted JavaScript libraries and safe
integration of mutually distrustful websites (mash-ups), may be
effectively addressed using an efficient implementation of information
flow control (IFC).  Unfortunately existing fine-grained approaches to
JavaScript IFC require modifications to the language semantics and its engine, a
non-goal for browser applications.  In this work, we take the ideas of
coarse-grained dynamic IFC and provide the theoretical
foundation for a language-based approach that can be applied to any
programming language for which external effects can be controlled.  We
then apply this formalism to JavaScript, in the context of Node.js and
Firefox, and show how it generalizes to the C programmings language.  Our methodology offers
design principles for the construction of information flow control
systems when isolation can easily be achieved, as well as
compositional proofs for optimized concrete implementations of these
systems, by relating them to their isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser
extension security, untrusted JavaScript libraries and safe
integration of mutually distrustful websites (mash-ups), may be
effectively addressed using an efficient implementation of information
flow control (IFC).  Unfortunately existing fine-grained approaches to
JavaScript IFC require modifications to the language semantics and its engine, a
non-goal for browser applications.  In this work, we take the ideas of
coarse-grained dynamic IFC and provide the theoretical
foundation for a language-based approach that can be applied to any
programming language for which external effects can be controlled.  We
then apply this formalism to server- and client-side JavaScript,
show how it generalizes to the C programmings language, and connect it
to the Haskell LIO system.  Our methodology offers
design principles for the construction of information flow control
systems when isolation can easily be achieved, as well as
compositional proofs for optimized concrete implementations of these
systems, by relating them to their isolated variants.
\end{abstract}
